Foregrounds in Wide--Field Redshifted 21~cm Power Spectra

### 2015-02-23 ms.tex
Specify cosmological parameters used in paper
from b87734d:
============

In ms.tex,

(*) Specify cosmological parameters used in S2
Address referee comments from second stage review
from 29407e6:
============

In ms.tex,

(*) Modify 3-baseline figure (figure 8) by removing gray shade showing
expected uncertainties. Modify caption accrodingly.
(*) Modify text describing figure 8 according to changes above
(*) Change "equivalent" to "related" in describing interpretations pf
the pitchfork effect in S3 and Summary

In order to express a quantity derived from $\tilde{V}_b(\tau)$ whose units are the same as that of the cosmological H{\sc i} power spectrum, we define the delay power spectrum:
\begin{align}\label{eqn:delay-power-spectrum}
  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{A_\textrm{e}}{\lambda^2\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{align}
where, $A_\textrm{e}$ is the effective area of the antenna, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2$(Mpc/$h$)$^3$.

@@

We interpret this as due to equal--sized delay bins subtending larger solid angles near the horizon thereby containing larger integrated emission. An alternate, but equivalent, interpretation is that baseline vectors (including those with largest lengths) are foreshortened towards the horizon along their orientation. Thus, they become sensitive to larger angular scales that match the inverse of their foreshortened lengths along these directions.

@@

Figure~\ref{fig:pitchfork-baselines} shows delay spectra of three antenna pairs of different antenna spacings oriented northward during the {\it zenith} pointing; each is a different vertical slice of the {\bf delay power spectra} plots shown in Figure~\ref{fig:noiseless-dsm-csm-delay-spectrum}. The diffuse, compact, and composite components are shown as solid red, cyan, and black lines, respectively. The horizon delay limits are shown as a pair of vertical dotted lines. The gray shaded area denotes the envelope of expected uncertainty in the {\bf delay power spectrum}. Uncertainty in emission in the {\it foreground} wedge (between the horizon delay limits) is dominated by the % $\gtrsim$~70\% error owing to 
uncertainty in predicting the spectral index of compact foreground model, while thermal noise fluctuations dominate outside.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure9.eps}
\includegraphics[width=\linewidth]{figure8.eps}
\caption{Simulated {\bf delay power spectra} for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The baseline length and orientation is specified in each panel. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. {\bf Compact emission dominates the central regions of the delay power spectra while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a characteristic {\it pitchfork}--shaped structure. The shaded region denotes the envelope of uncertainty around the composite model delay power spectrum. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits and by thermal noise fluctuations outside}. \label{fig:pitchfork-baselines}}
\end{figure}

@@

{\bf We find that all wide--field instruments, typical of modern EoR observatories, imprint a characteristic {\it two--pronged fork} signature in delay spectra. There are two equivalent interpretations: delay bins near the horizon subtend larger solid angles and therefore contain larger integrated emission; or, foreshortening of baselines towards the horizon makes them sensitive to emission on large angular scales which match the inverse of their foreshortened lengths. These effects combined with higher sensitivity of antennas in the primary field of view results in a characteristic {\it pitchfork} signature. The amplitude of these generic signatures can be controlled by careful design of antenna aperture. In contrast to a dipole and a phased array such as an MWA tile, a dish such as the one proposed for HERA is found to yield the least foreground contamination and thus preferable for EoR studies.}

>>>>

In order to express a quantity derived from $\tilde{V}_b(\tau)$ whose units are the same as that of the cosmological H{\sc i} power spectrum, we define the delay power spectrum:
\begin{align}\label{eqn:delay-power-spectrum}
  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{A_\textrm{e}}{\lambda^2\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
\end{align}
where, $A_\textrm{e}$ is the effective area of the antenna, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. Throughout the paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2$(Mpc/$h$)$^3$.

@@

We interpret this as due to equal--sized delay bins subtending larger solid angles near the horizon thereby containing larger integrated emission. An alternate, but related, interpretation is that baseline vectors (including those with largest lengths) are foreshortened towards the horizon along their orientation. Thus, they become sensitive to larger angular scales that match the inverse of their foreshortened lengths along these directions.

@@

Figure~\ref{fig:pitchfork-baselines} shows delay spectra of three antenna pairs of different antenna spacings oriented northward during the {\it zenith} pointing; each is a different vertical slice of the {\bf delay power spectra} plots shown in Figure~\ref{fig:noiseless-dsm-csm-delay-spectrum}. The diffuse, compact, and composite components are shown as solid red, cyan, and black lines, respectively. The horizon delay limits are shown as a pair of vertical dotted lines. % The gray shaded area denotes the envelope of expected uncertainty in the {\bf delay power spectrum}. Uncertainty in emission in the {\it foreground} wedge (between the horizon delay limits) is dominated by the % $\gtrsim$~70\% error owing to 
% uncertainty in predicting the spectral index of compact foreground model, while thermal noise fluctuations dominate outside.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure9.eps}
\includegraphics[width=\linewidth]{figure8.eps}
\caption{Simulated {\bf delay power spectra} for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The baseline length and orientation is specified in each panel. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. {\bf Compact emission dominates the central regions of the delay power spectra while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a characteristic {\it pitchfork}--shaped structure. % The shaded region denotes the envelope of uncertainty around the composite model delay power spectrum. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits and by thermal noise fluctuations outside
} \label{fig:pitchfork-baselines}}
\end{figure}

@@

{\bf We find that all wide--field instruments, typical of modern EoR observatories, imprint a characteristic {\it two--pronged fork} signature in delay spectra. There are two related interpretations: delay bins near the horizon subtend larger solid angles and therefore contain larger integrated emission; and, foreshortening of baselines towards the horizon makes them sensitive to emission on large angular scales which match the inverse of their foreshortened lengths. These effects combined with higher sensitivity of antennas in the primary field of view results in a characteristic {\it pitchfork} signature. The amplitude of these generic signatures can be controlled by careful design of antenna aperture. In contrast to a dipole and a phased array such as an MWA tile, a dish such as the one proposed for HERA is found to yield the least foreground contamination and thus preferable for EoR studies.}
